parental migration and adolescents educational performance

### 2022-06-21 data/Gu-thesis-script.Rmd
write up main text, set matching criteria, add summary tables

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
library(datawizard)
```

## Data cleaning
Read CEPS data
```{r}
d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
d_stu2 <- read_dta('cepsw2studentCN.dta') #wave 2 student
d_par1 <- read_dta('cepsw1parentCN.dta') #wave 1 parent
d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
d_sch2 <- read_dta('cepsw2principalCN.dta')
```

@@

Assemble a panel dataset in wide format
```{r}
dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) %>% left_join(d_sch1, by=c('schids', 'ctyids', 'fall'))
dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

```{r}
d <- d %>% mutate(
  age = 2013 - a02a, #student's age at baseline
  local.resi = age - a07, #years of residence at the current county
  w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
  w1mat_100 = tr_mat/w2upmat*100,
  w1eng_100 = tr_eng/w2upeng*100,
  w2chn_100 = w2chn/w2upchn*100,
  w2mat_100 = w2mat/w2upmat*100,
  w2eng_100 = w2eng/w2upeng*100
)
d <- d %>% mutate(
  w1ttl_100 = w1chn_100 + w1mat_100 + w1eng_100,
  w2ttl_100 = w2chn_100 + w2mat_100 + w2eng_100,
  )
```

Detect outliers
```{r}
d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

Compute standardized exam grades (within-school z-scores)
```{}
d1 <- d1 %>% #Within-school standardization for Chinese, math, English exams and their total, respectively
  group_by(schids) %>%
  mutate(w1chn_mean = mean(w1chn_100, na.rm=T),
         w1mat_mean = mean(w1mat_100, na.rm=T),
         w1eng_mean = mean(w1eng_100, na.rm=T),
         w1ttl_mean = mean(w1ttl_100, na.rm=T),
         w2chn_mean = mean(w2chn_100, na.rm=T),
         w2mat_mean = mean(w2mat_100, na.rm=T),
         w2eng_mean = mean(w2eng_100, na.rm=T),
         w2ttl_mean = mean(w2ttl_100, na.rm=T),
         )  %>% ungroup()
```

```{}
d1 <- d1 %>% 
  mutate(w1chn_dif = w1chn_100 - w1chn_mean,
         w1mat_dif = w1mat_100 - w1mat_mean,
         w1eng_dif = w1eng_100 - w1eng_mean,
         w1ttl_dif = w1ttl_100 - w1ttl_mean,
         w2chn_dif = w2chn_100 - w2chn_mean,
         w2mat_dif = w2mat_100 - w2mat_mean,
         w2eng_dif = w2eng_100 - w2eng_mean,
         w2ttl_dif = w2ttl_100 - w2ttl_mean,

         )
```

Sample
```{r}
d_cl <- d1 %>% 
  filter(w2a0801==1) %>% #parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #both parents live with children at baseline
  filter(stmigrant==1) #having stayed in the current county for at least six years (duration of primary school) before baseline
```

## Variables 
```{r}
d_cl <- d_cl %>% 
  mutate(chn_dif = w2chn_100 - w1chn_100,
         mat_dif = w2mat_100 - w1mat_100,
         eng_dif = w2eng_100 - w1eng_100,
         ttl_dif = w2ttl_100 - w1ttl_100,
         cog_dif = w2cog3pl - cog3pl) %>%
  drop_na(cog_dif, chn_dif, mat_dif, eng_dif, ttl_dif)
```

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         ch.girl = if_else(a01 == 2, 1, 0), #student is girl
         ch.rural = sthktype, #student holds rural (agricultural) hukou
         #ch.only.child = if_else(b01 == 1, 1, 0), #student is only child
         ch.boarding = stbrd, #student is boarding at school
         ch.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
         ch.health = a17, #student's self-reported health
         ch.skip.grd = if_else(c03 == 0, 0, 1),
         ch.repeat.grd = if_else(c04 == 0, 0, 1),
         ch.illness = if_else(a10 == 1, 1, 0),
         ch.preschool = if_else(c01 == 1, 1, 0),
         par.edu = stprhedu, #Among two parents, the best-educated one's educational level
         par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
         home.finances = steco_3c,
         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.book = b12 #Amount of book at home, student self-rated 
) %>% drop_na(
ch.girl, ch.rural, ch.health, ch.boarding, ch.ethn.minority, ch.health, ch.skip.grd, ch.repeat.grd, ch.illness, ch.preschool, par.edu, par.ccp, home.internet, home.book, home.finances)
```

```{r}
d_cl$stsib <- d_cl$stsib %>% replace_na(0) %>% as.numeric()
d_cl <- d_cl %>% mutate(ch.sibling = if_else(stonly == 1, 0, stsib)) %>% #number of siblings
  drop_na(ch.sibling)
```

Best-educated parent's years of education
```{r}
d_cl <- d_cl %>% mutate(par.edu.year = NA)
d_cl$par.edu.year[d_cl$par.edu == 1] <- 0
d_cl$par.edu.year[d_cl$par.edu == 2] <- 6
d_cl$par.edu.year[d_cl$par.edu == 3] <- 9
d_cl$par.edu.year[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
d_cl$par.edu.year[d_cl$par.edu == 7] <- 15
d_cl$par.edu.year[d_cl$par.edu == 8] <- 16
d_cl$par.edu.year[d_cl$par.edu == 9] <- 19
```

```
d_cl <- d_cl %>% mutate(fa.edu.year = NA)
d_cl$fa.edu.year[d_cl$fa.edu == 1] <- 0
d_cl$fa.edu.year[d_cl$fa.edu == 2] <- 6
d_cl$fa.edu.year[d_cl$fa.edu == 3] <- 9
d_cl$fa.edu.year[d_cl$fa.edu == 4|d_cl$fa.edu == 5|d_cl$fa.edu == 6] <- 12
d_cl$fa.edu.year[d_cl$fa.edu == 7] <- 15
d_cl$fa.edu.year[d_cl$fa.edu == 8] <- 16
d_cl$fa.edu.year[d_cl$fa.edu == 9] <- 19
```

```
d_cl <- d_cl %>% mutate(mo.edu.year = NA)
d_cl$mo.edu.year[d_cl$mo.edu == 1] <- 0
d_cl$mo.edu.year[d_cl$mo.edu == 2] <- 6
d_cl$mo.edu.year[d_cl$mo.edu == 3] <- 9
d_cl$mo.edu.year[d_cl$mo.edu == 4|d_cl$mo.edu == 5|d_cl$mo.edu == 6] <- 12
d_cl$mo.edu.year[d_cl$mo.edu == 7] <- 15
d_cl$mo.edu.year[d_cl$mo.edu == 8] <- 16
d_cl$mo.edu.year[d_cl$mo.edu == 9] <- 19
```

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl %>% mutate(
  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
  migr_fa_only = NA,
  migr_fa = NA,
  migr_mo_only = NA,
  migr_mo = NA,
  migr_both = NA
  ) 
d_cl <- d_cl %>% drop_na(migr)
```

@@

Mother migrated
```{r}
d_cl$migr_mo[d_cl$migr == 0] <- 0
d_cl$migr_mo[d_cl$w2ba0202==0] <- 1
```

@@

Father migrated
```{r}
d_cl$migr_fa[d_cl$migr == 0] <- 0
d_cl$migr_fa[d_cl$w2ba0201==0] <- 1
```

@@

```
df <- d_cl %>% select(
  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
  cog3pl, w1chn_dif, w1mat_std, w1eng_std,
  cog, chn_std, mat_dif, eng_dif,
  age, ch.girl, ch.health, ch.rural, ch.sibling, ch.boarding, ch.ethn.minority, 
  par.edu.year, home.book, home.internet
)
```

t-test
```{r}
t.test(cog_dif ~ migr, data = d_cl)
t.test(ttl_dif ~ migr, data = d_cl)
t.test(chn_dif ~ migr, data = d_cl)
t.test(mat_dif ~ migr, data = d_cl)
t.test(eng_dif ~ migr, data = d_cl)
```

## Descriptive statistics
```{r}
des_gender <- d_cl %>% count(ch.girl)
des_rural <- d_cl %>% count(ch.rural)
des_sibling <- d_cl %>% group_by(ch.sibling) %>% count
des_boarding <- d_cl %>% count(ch.boarding)
des_book <- d_cl %>% group_by(home.book) %>% count
des_internet <- d_cl %>% group_by(home.internet) %>% count
des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
des_ethn.minority <- d_cl %>% group_by(ch.ethn.minority) %>% count
des_gender
des_rural
des_sibling
des_boarding
des_par.edu.year
des_book
des_internet
des_ethn.minority
```

### Wave 2 outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_dif, na.rm=T),
            mean_chn = mean(w2chn_dif, na.rm=T),
            mean_mat = mean(w2mat_dif, na.rm=T),
            mean_eng = mean(w2eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

### Change in outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog_dif, na.rm=T),
            mean_change_ttl = mean(ttl_dif, na.rm=T),
            mean_change_chn = mean(chn_dif, na.rm=T),
            mean_change_mat = mean(mat_dif, na.rm=T),
            mean_change_eng = mean(eng_dif, na.rm=T)
            ) %>%
  drop_na()
```

## DID unrestricted
Regressing on cognitive test score (standardized)
```{r}
did_unres_cog <- feols(cog_dif ~ migr + cog3pl | schids, data = d_cl) 
did_unres_cog_m_only <- feols(cog_dif ~ migr_mo_only + cog3pl | schids, data = d_cl) 
did_unres_cog_m <- feols(cog_dif ~ migr_mo + cog3pl | schids, data = d_cl) 
did_unres_cog_f_only <- feols(cog_dif ~ migr_fa_only + cog3pl | schids, data = d_cl) 
did_unres_cog_f <- feols(cog_dif ~ migr_fa + cog3pl | schids, data = d_cl) 
did_unres_cog_both <- feols(cog_dif ~ migr_both + cog3pl | schids, data = d_cl)
```

Results
```{r}
models_unres_cog <- list(
'Any Parent Absent' = did_unres_cog,
'Only Mother Absent' = did_unres_cog_m_only,
'Mother Absent' = did_unres_cog_m,
'Only Father Absent' = did_unres_cog_f_only,
'Father Absent' = did_unres_cog_f,
'Both Parents Absent' = did_unres_cog_both) 
table_unres_cog <- models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), 
                              fmt = 2,
                              coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator", "cog3pl" = "Baseline Score"), output = 'markdown')
table_unres_cog
```

>>>>

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
#library(vtable)
library(ggplot2)
library(gtsummary)
#library(DescTools)
```

## Data cleaning
Read CEPS data
```{r}
d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
d_stu2 <- read_dta('cepsw2studentCN.dta') #wave 2 student
d_par1 <- read_dta('cepsw1parentCN.dta') #wave 1 parent
d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
#d_sch1 <- read_dta('cepsw1principalCN.dta') #wave 1 school principal
#d_sch2 <- read_dta('cepsw2principalCN.dta')
```

@@

Assemble a panel dataset in wide format
```{r}
dw1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) 
dw2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- dw1 %>% right_join(dw2, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

```{r}
d <- d %>% mutate(
  child.age = 2013 - a02a, #student's age at baseline
  w1chn_100 = tr_chn/w2upchn*100, #raw exam scores at 100-point scale
  w1mat_100 = tr_mat/w2upmat*100,
  w1eng_100 = tr_eng/w2upeng*100,
  w2chn_100 = w2chn/w2upchn*100,
  w2mat_100 = w2mat/w2upmat*100,
  w2eng_100 = w2eng/w2upeng*100
)
```

```{}
set.seed(1)
d %>% select(
  w1chn_100:w2eng_100) %>%
ggplot(aes(x=w1chn_100:w2eng_100)) + 
  geom_boxplot(alpha=0.2)
```

Trimming outliers
```{r}
d <- d %>% mutate(
  w1chn_100_trim = if_else(w1chn_100>100, 100, w1chn_100),
  w2chn_100_trim = if_else(w2chn_100>100, 100, w2chn_100),
  w1mat_100_trim = if_else(w1mat_100>100, 100, w1mat_100),
  w2mat_100_trim = if_else(w2mat_100>100, 100, w2mat_100),
  w1eng_100_trim = if_else(w1eng_100>100, 100, w1eng_100),
  w2eng_100_trim = if_else(w2eng_100>100, 100, w2eng_100)
)
```

```{r}
d <- d %>% mutate(
  w1ttl_100 = w1chn_100_trim + w1mat_100_trim + w1eng_100_trim,
  w2ttl_100 = w2chn_100_trim + w2mat_100_trim + w2eng_100_trim,
  ttl_dif = w2ttl_100 - w1ttl_100,
  cog_dif = w2cog3pl - cog3pl
  )
```

```{r}
d1 <- d %>%
  drop_na(cog_dif, ttl_dif, child.age)
```

within-class z score
```{}
d1 <- d1 %>% group_by(clsids + w2clsids) %>%
  mutate(
    w1ttl_z = as.numeric(scale(w1ttl)),
    w2ttl_z = as.numeric(scale(w2ttl))
  ) %>% ungroup()
```

```{}
d1 <- d1 %>% group_by(clsids + w2clsids) %>%
  mutate(
    w1ttl_std = rescale(w1ttl),
    w2ttl_std = rescale(w2ttl)
    ) %>% ungroup()
```

Detect outliers
```{}
d_outlier <- d %>% filter(w1chn_100 > 100 | w1mat_100>100|w1eng_100>100|w2chn_100>100|w2mat_100>100|w2eng_100>100)
d_outlier1 <- d_outlier %>% select(clsids, clsids + w2clsids, tr_chn, tr_mat, tr_eng, w2chn, w2upchn, w2mat, w2upmat, w2eng, w2upeng)
d1 <- d %>% anti_join(d_outlier, by=c('ids', 'clsids', 'clsids + w2clsids', 'ctyids'))
```

Sample
```{r}
d_cl <- d1 %>% 
  filter(w2a0801==1) %>% #keep parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #keep both parents live with children at baseline
  filter(stmigrant==1) #keep local children 
```

## Variables

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         child.is.girl = if_else(a01 == 2, 1, 0), #student is girl
         child.has.rural.hukou = sthktype, #student holds rural (agricultural) hukou
         child.in.boarding.school = stbrd, #student is boarding at school
         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
         child.health.self.rated = a17, #student's self-rated health
         child.had.skipped.grade = if_else(c03 == 0, 0, 1), #student had skipped grade
         child.had.repeated.grade = if_else(c04 == 0, 0, 1), #student had repeated grade
         #ch.illness = if_else(a10 == 1, 1, 0), #student had serious illness before primary school
         child.went.to.preschool = if_else(c01 == 1, 1, 0), #student had attended preschool
         #ch.par.rltn = if_else(stprrel == 2, 1, 0),
         #ch.tutoring = if_else(b1901 == 1|b1902 == 1|b1903 == 1|b1904 == 1, 1, 0),
         par.edu = stprhedu, #Among two parents, the best-educated one's educational level
         parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
         #par.ccp = if_else(be06 == 1, 1, 0), #At least one parent is communist party member
         home.economic.resource = steco_5c, #self-rated household financial situation
         home.has.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.extracurricular.book = b12 #Amount of book at home, student self-rated 
) %>% drop_na(
child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, par.edu, 
#par.ccp, 
parent.has.white.collar.job, home.has.internet, home.extracurricular.book, home.economic.resource)
```

```{r}
d_cl$stsib <- d_cl$stsib %>% replace_na(0) %>% as.numeric()
d_cl <- d_cl %>% mutate(child.number.of.sibling = if_else(stonly == 1, 0, stsib)) %>% #number of siblings
  drop_na(child.number.of.sibling)
```

Best-educated parent's years of education
```{}
d_cl <- d_cl %>% mutate(parent.educational.level = NA)
d_cl$parent.educational.level[d_cl$par.edu == 1] <- 0
d_cl$parent.educational.level[d_cl$par.edu == 2] <- 6
d_cl$parent.educational.level[d_cl$par.edu == 3] <- 9
d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
d_cl$parent.educational.level[d_cl$par.edu == 7] <- 15
d_cl$parent.educational.level[d_cl$par.edu == 8] <- 16
d_cl$parent.educational.level[d_cl$par.edu == 9] <- 19
```

```{r}
d_cl <- d_cl %>% mutate(parent.educational.level = NA)
d_cl$parent.educational.level[d_cl$par.edu == 1|d_cl$par.edu == 2] <- 1
d_cl$parent.educational.level[d_cl$par.edu == 3] <- 2
d_cl$parent.educational.level[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 3
d_cl$parent.educational.level[d_cl$par.edu == 7] <- 4
d_cl$parent.educational.level[d_cl$par.edu == 8] <- 5
d_cl$parent.educational.level[d_cl$par.edu == 9] <- 6
```

```{r}
d_cl <- d_cl %>% mutate(parent.expectation.on.child = NA)
d_cl$parent.expectation.on.child[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
d_cl$parent.expectation.on.child[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
d_cl$parent.expectation.on.child[d_cl$ba18 == 6] <- 3
d_cl$parent.expectation.on.child[d_cl$ba18 == 7] <- 4
d_cl$parent.expectation.on.child[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
```

```{r}
d_cl <- d_cl %>% mutate(child.educational.aspiration = NA)
d_cl$child.educational.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
d_cl$child.educational.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
d_cl$child.educational.aspiration[d_cl$c22 == 6] <- 3
d_cl$child.educational.aspiration[d_cl$c22 == 7] <- 4
d_cl$child.educational.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
```

```{r}
d_cl <- d_cl %>%  drop_na(
  parent.educational.level, 
  parent.expectation.on.child, 
  child.educational.aspiration)
```

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl %>% mutate(
  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
  migr_fa_only = NA,
  #migr_fa = NA,
  migr_mo_only = NA,
  #migr_mo = NA,
  migr_both = NA
  ) %>% drop_na(migr)
```

@@

Mother migrated
```{}
d_cl$migr_mo[d_cl$migr == 0] <- 0
d_cl$migr_mo[d_cl$w2ba0202==0] <- 1
```

@@

Father migrated
```{}
d_cl$migr_fa[d_cl$migr == 0] <- 0
d_cl$migr_fa[d_cl$w2ba0201==0] <- 1
```

@@

```{}
df <- d_cl %>% select(
  migr, migr_fa_only, migr_fa, migr_mo_only, migr_mo, migr_both,
  cog3pl, w1ttl_100, cog_dif, ttl_dif,
  child.is.girl, child.has.rural.hukou, child.health.self.rated, child.in.boarding.school, child.is.ethnic.minority, child.health.self.rated, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.educational.aspiration, 
  par.edu, par.ccp, par.expt.univ, 
  home.has.internet, home.extracurricular.book, home.economic.resource
)
```

## Descriptive statistics
```{r}
d_migr <- d_cl %>%
  select(
  migr, migr_mo_only, migr_fa_only, migr_both,
  cog3pl, w2cog3pl, w1ttl_100, w2ttl_100, cog_dif, ttl_dif,
  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
  child.health.self.rated, child.educational.aspiration, 
  parent.educational.level, parent.expectation.on.child, 
  home.extracurricular.book, home.economic.resource) %>%
  remove_labels()
```

```{r}
d_smr <- d_migr %>% 
  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) %>% 
  mutate(`Parental Migration Type` = 0) 
d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother Migrated'
d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father Migrated'
d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents Migrated'
d_smr <- d_smr %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

```{r}
datasummary_balance(
  ~migr,
  data = d_migr,
  fmt = 2)
```

```{r}
d_dpvar <- d_migr %>%
  select(migr, 
         cog_dif, cog3pl, w2cog3pl, ttl_dif, w1ttl_100, w2ttl_100) %>%
  rename(
    `Cognitive score at wave 1` = cog3pl,
    `Cognitive score at wave 2` = w2cog3pl,
    `Academic exam score at wave 1` = w1ttl_100,
    `Academic exam score at wave 2` = w2ttl_100,
    `Cognitive score difference` = cog_dif,
    `Academic exam score difference` = ttl_dif
  ) 
```

```{}
d_dpvar %>%
  tbl_summary(
    by = migr,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} / {N} ({p}%)"),
    digits = all_continuous() ~ 2,
    ) %>% add_p() %>% as_kable()
```

```{r}
#table_independent_variable <- 
  st(
  d_dpvar,
  digits = 2, 
  group = 'migr',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = 'kable')
#table_independent_variable 
```

```{r}
d_dpvar <- as.data.frame(d_dpvar)
table_dependent_variable <- datasummary(
  All(d_dpvar) ~ Mean + SD + Min + Max,
  data = d_dpvar,
  output = 'markdown'
  )
```

```{r}
table_independent_variable <- datasummary_skim(
    data=d_idpvar,
    type = 'categorical',
    output = 'markdown')

```

```{r}
d_idpvar <- d_migr %>% 
  select(migr, migr_mo_only, migr_fa_only, migr_both) %>% 
  mutate(`Parental Migration` = if_else((migr==1), 'Yes', 'No')) %>% 
  mutate(`Parental Migration Type` = 0) 
d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents At Home'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
d_idpvar <- d_idpvar %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

```{r}

```

```{r}
d_ctvar <- d_migr %>%
  select(migr, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet,
  child.health.self.rated, child.educational.aspiration, 
  parent.educational.level, parent.expectation.on.child, 
  home.extracurricular.book, home.economic.resource) %>% 
  mutate_if(is.numeric, as.factor)
```

```{r}
d_ctvar$parent.educational.level <- d_ctvar$parent.educational.level %>% 
  recode_factor(
    '1' = 'Primary school and below',
    '2' = 'Junior high school',
    '3' = 'Senior high school',
    '4' = 'Associate college',
    '5' = 'University',
    '6' = 'Postgraduate'
  )
d_ctvar$child.educational.aspiration <- d_ctvar$child.educational.aspiration %>%
  recode_factor(
    '1' = 'Junior high school',
    '2' = 'Senior high school',
    '3' = 'Associate college',
    '4' = 'University',
    '5' = 'Postgraduate'     
  )
d_ctvar$parent.expectation.on.child  <- d_ctvar$parent.expectation.on.child %>%
  recode_factor(
    '1' = 'Junior high school',
    '2' = 'Senior high school',
    '3' = 'Associate college',
    '4' = 'University',
    '5' = 'Postgraduate'    
  )
d_ctvar$home.economic.resource <- d_ctvar$home.economic.resource %>% 
  recode_factor(
    '1' = 'Very poor',
    '2' = 'Somewhat poor',
    '3' = 'Moderate',
    '4' = 'Somewhat rich',
    '5' = 'Very rich'
  )
d_ctvar$child.health.self.rated <- d_ctvar$child.health.self.rated %>%
  recode_factor(
    '1' = 'Very poor',
    '2' = 'Not very good',
    '3' = 'Moderate',
    '4' = 'Good',
    '5' = 'Very good'
  )
d_ctvar$home.extracurricular.book <- d_ctvar$home.extracurricular.book %>%
  recode_factor(
    '1' = 'Very few',
    '2' = 'Not many',
    '3' = 'Some',
    '4' = 'Quite a few',
    '5' = 'A great number'
  )
```

```{}
test.table <- d_ctvar %>%
  tbl_summary(
    by = migr,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    ) 
```

```{r}
test_table <- datasummary_balance(
  ~migr,
  data = d_ctvar
)
test_table
```

```{r}
#table_control_variable <- 
table_balance <- st(
  d_ctvar,
  digits = 2, 
  group = 'migr',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = "return")
#table_control_variable 
```

```{r}
table_control_variable <- datasummary_skim(
  data = d_ctvar,
  type = 'categorical',
  output = 'markdown'
)
```

```{r}
d_migr <- d_migr %>% mutate(`Parental Migration` = ifelse(migr == 1, 'Yes', 'No'))
d_migr <- d_migr %>% mutate(`Parental Migration Type` = 0) 
d_migr$`Parental Migration Type`[d_migr$migr==0] <- 'Both Parents At Home'
d_migr$`Parental Migration Type`[d_migr$migr_mo_only==1] <- 'Only Mother Migrated'
d_migr$`Parental Migration Type`[d_migr$migr_fa_only==1] <- 'Only Father Migrated'
d_migr$`Parental Migration Type`[d_migr$migr_both==1] <- 'Both Parents Migrated'
d_migr <- d_migr %>% select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

Whole sample summary
```{r}
table_sum <- st(
  d_migr,
  digits = 2, 
  out = 'kable')
table_sum
```

```{r}
table_sum_migr <- st(
  d_migr,
  group = 'Parental Migration', 
  digits = 2, 
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = 'kable')
table_sum_migr
```

t-test
```{r}
ttest_cog <- t.test(cog_dif ~ migr, data = d_cl)
ttest_ttl <- t.test(ttl_dif ~ migr, data = d_cl)
ttest_cog
ttest_ttl
```

```{r}
set.seed(1)
fig_cog <- 
  ggplot(d_migr, aes(x='Parental Migration Type', y=cog_dif, fill = `Parental Migration`)) + 
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    geom_boxplot(alpha=0.2)
```
